\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-28 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updates

To account the pertinent geometry of $\mathbb{T}^{n}\times\mathbb{R}^{n}$, we take the initial joint PDF as
\begin{align}
\rho_{0}&\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \vartheta_{0}\left(\bm{\theta}(0)\right)\Omega_{0}\left(\bm{\omega}(0)\right)\nonumber\\
&=\underbrace{\left(\prod_{i=1}^{n=5}\dfrac{\exp\left(\kappa_{i}\cos\left(2\theta_{i}(0)-\mu_{\theta_{i}(0)}\right)\right)}{2\pi I_{0}(\kappa_{i})}\right)}_{=:\vartheta_{0}\left(\bm{\theta}(0)\right)}\nonumber\\
	&\qquad\times \underbrace{{\rm{Unif}}\left([-0.1,0.1]\;\text{rad/s}\right)}_{=:\Omega_{0}\left(\bm{\omega}(0)\right)},
\label{rho0IEEE14}		
\end{align}
whose $\bm{\theta}$ marginal $ \vartheta_{0}\left(\bm{\theta}(0)\right)$ is a product von Mises PDF\footnote{the factor $2$ inside the cosine ensures the range $[0,2\pi)$; it can be dispensed if we instead use the range $[-\pi,\pi)$ for the angular variables, as common in the directional statistics literature \cite{mardia2009directional}.} \cite{mardia2008multivariate,mardia2014some} supported over $\mathbb{T}^{5}$ with mean angles (in rad)
\begin{align}
\left(\mu_{\theta_{1}}(0),\hdots,\mu_{\theta_{5}}(0)\right)=\left(0, 6.1963, 6.0612, 6.0350, 6.0500\right),
\label{MeanAngleInitialIEEE14}	
\end{align}
and concentration parameter $\kappa_{i}\geq 0$ set as 
\[(\kappa_{1},\hdots,\kappa_5) = \left(5,6,7,4,5\right).\]
In \eqref{rho0IEEE14}, $I_{0}(\cdot)$ denotes the modified Bessel function of the first kind with order zero, given by $I_{0}(\kappa) = \sum_{r=0}^{\infty} \frac{\left(\kappa^{2}/4\right)^{r}}{(r!)^{2}}$, and can be evaluated via MATLAB command \texttt{besseli(0,$\cdot$)}.

@@

In \eqref{rho0IEEE14}, the $\bm{\omega}$ marginal $ \Omega_{0}\left(\bm{\omega}(0)\right)$ is a uniform PDF over $[-0.1,0.1]$ rad/s. Thus, the PDF $\rho_0$ in \eqref{rho0IEEE14} is supported over $\mathbb{T}^{5}\times [-0.1,0.1]$.

>>>>

To account the pertinent geometry of $\mathbb{T}^{n}\times\mathbb{R}^{n}$, we take the initial joint PDF as
\begin{align}
\rho_{0}&\equiv\rho(t=0,\bm{\theta}(0),\bm{\omega}(0)) = \vartheta_{0}\left(\bm{\theta}(0)\right)\Omega_{0}\left(\bm{\omega}(0)\right)\nonumber\\
&=\underbrace{\left(\prod_{i=1}^{n=5}\dfrac{\exp\left(\kappa_{i}\cos\left(2\theta_{i}(0)-\mu_{\theta_{i}(0)}\right)\right)}{2\pi I_{0}(\kappa_{i})}\right)}_{=:\vartheta_{0}\left(\bm{\theta}(0)\right)}\nonumber\\
	&\qquad\times \underbrace{{\rm{Unif}}\left(\left([-0.1,0.1]\;\text{rad/s}\right)^{5}\right)}_{=:\Omega_{0}\left(\bm{\omega}(0)\right)},
\label{rho0IEEE14}		
\end{align}
whose $\bm{\theta}$ marginal $ \vartheta_{0}\left(\bm{\theta}(0)\right)$ is a product von Mises PDF\footnote{the factor $2$ inside the cosine ensures the range $[0,2\pi)$; it can be dispensed if we instead use the range $[-\pi,\pi)$ for the angular variables, as common in the directional statistics literature \cite{mardia2009directional}.} \cite{mardia2008multivariate,mardia2014some} supported over $\mathbb{T}^{5}$ with mean angles (in rad)
\begin{align}
\left(\mu_{\theta_{1}}(0),\hdots,\mu_{\theta_{5}}(0)\right)=\left(0, 6.1963, 6.0612, 6.0350, 6.0500\right),
\label{MeanAngleInitialIEEE14}	
\end{align}
and concentration parameter $\kappa_{i}\geq 0$ set as 
\[(\kappa_{1},\hdots,\kappa_5) = \left(5,6,7,4,5\right).\]
In \eqref{rho0IEEE14}, $I_{0}(\cdot)$ denotes the modified Bessel function of the first kind with order zero, given by $I_{0}(\kappa) = \sum_{r=0}^{\infty} \frac{\left(\kappa^{2}/4\right)^{r}}{(r!)^{2}}$, and can be evaluated via MATLAB command \texttt{besseli(0,$\cdot$)}.

@@

In \eqref{rho0IEEE14}, the $\bm{\omega}$ marginal $ \Omega_{0}\left(\bm{\omega}(0)\right)$ is a uniform PDF over the hypercube $\left([-0.1,0.1]\;\text{rad/s}\right)^{5}$. Thus, the PDF $\rho_0$ in \eqref{rho0IEEE14} is supported over $\mathbb{T}^{5}\times [-0.1,0.1]^{5}$.
